---
title: "DDP Week 4 Course Project"
author: "Fergus Meade"
date: "10/25/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr); library(pxR); library(ggplot2)
```

## Overview
The goal is to create a simple shiny application to allow a user to examine changes in crop value/output in Ireland over time. Data on agricultural output is obtained from Ireland's Central Statistics Office and filtered for crop data only.

The app allows the user to plot individual lines from the plot on slide 5 i.e. select a crop of interest.

## Data set

```{r data, echo = TRUE, warning=FALSE, message=FALSE}
url <- "http://www.cso.ie/px/pxeirestat/Database/Eirestat/Regional%20Accounts/ACA03.px"
ACA03df <- as.data.frame(read.px(url))
head(levels(ACA03df$Statistic)) #dataset contains 40 measures of agri output
levels(ACA03df$Year) #over the period 2010-2017
Crops <- ACA03df %>% 
    filter(Statistic %in% levels(ACA03df$Statistic)[10:16]) %>% #restrict to data about crops
    filter(Region == "State") #ignore regional data
```

## Retrieve information related to Crops

- Shiny app : https://fergusmeade.shinyapps.io/Crops_fm/
- Code : 
- Pitch :

-Input Panel: Select your crop group of interest
-Ouput Panel: A time series plot showing the change in value of the crop over time

## Plot

This plot obscures the growth in the value of fresh fruit and vegetable crops in recent years because these crops are still dwarved by forage. 

```{r echo=FALSE}
library(ggplot2)
ggplot(Crops, aes(x = Year, y = value, 
                  group = Statistic, colour = Statistic)) + 
  geom_line() + ylab(label="Millions of Euro") + xlab("Year") +
  theme_minimal()
```

